\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-11-26 paper/manuscript.tex
starting to add the LDA stuff to the new state-agnostic scripts

%topicweights density
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
	\label{doctopics_density}
	\includegraphics[width=\linewidth]{figures/doctopics_density.pdf}
\end{figure}

@@

%topicweights density
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
	\label{topicweights_density}
	\includegraphics[width=\linewidth]{figures/topicweights_density.pdf}
\end{figure}

@@

%size of the differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{diffsize}
	\includegraphics[width=\linewidth]{figures/diffsize.pdf}
\end{figure}

@@

%word topic probabilities for topics with big differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{plotWTP_bigdiffs}
	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs.pdf}
\end{figure}

@@

%word topic probabilities for topics with big differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{doctopics_density_bigdiffs}
	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs.pdf}
\end{figure}

@@

%Heatmaps
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{heatmaps_weights}
	\includegraphics[width=\linewidth]{figures/heatmaps_weights.png}
\end{figure}

>>>>

%topicweights density
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
	\label{doctopics_density}
	\includegraphics[width=\linewidth]{figures/doctopics_density_IN.pdf}
\end{figure}

@@

%topicweights density
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
	\label{topicweights_density}
	\includegraphics[width=\linewidth]{figures/topicweights_density_IN.pdf}
\end{figure}

@@

%size of the differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences (Indiana).}
	\label{diffsize}
	\includegraphics[width=\linewidth]{figures/diffsize_IN.pdf}
\end{figure}

@@

%word topic probabilities for topics with big differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{plotWTP_bigdiffs}
	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs_IN.pdf}
\end{figure}

@@

%word topic probabilities for topics with big differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{doctopics_density_bigdiffs}
	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs_IN.pdf}
\end{figure}

@@

%Heatmaps
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
	\label{heatmaps_weights}
	\includegraphics[width=\linewidth]{figures/heatmaps_weights_IN.png}
\end{figure}
